Self Regulation Ontology Retest Data Report

### 2017-04-12 SRO_Report.Rmd
reran report with replaced hddm parameters

```{r echo=FALSE}
get_labels = function(plot_df, ref_df, bin_col, group_col){

@@

```{r}
match_t1_t2 <- function(dv_var, t1_df = test_data, t2_df = retest_data, merge_var = 'sub_id'){
  df = merge(t1_df[,c(merge_var, dv_var)], t2_df[,c(merge_var, dv_var)], by = merge_var)
  df = df %>% 
    na.omit()%>%
    gather(dv, score, -sub_id) %>%
    mutate(time = ifelse(grepl('\\.x', dv), 1, ifelse(grepl('\\.y', dv), 2, NA))) %>%
    separate(dv, c("dv", "drop"), sep='\\.([^.]*)$') %>%
    select(-drop)
   return(df)
}

get_icc <- function(dv_var, t1_df = test_data, t2_df = retest_data, merge_var = 'sub_id'){
  df = match_t1_t2(dv_var, t1_df = t1_df, t2_df = t2_df, merge_var = merge_var)
  df = df %>% spread(time, score) %>% select(-dv, -sub_id)
  icc = ICC(df)
  icc_3k = icc$results['Average_fixed_raters', 'ICC']
  return(icc_3k)
  }

get_eta <- function(dv_var, t1_df = test_data, t2_df = retest_data, merge_var = 'sub_id'){
  df = match_t1_t2(dv_var, t1_df = t1_df, t2_df = t2_df, merge_var = merge_var)
  mod = summary(aov(score~Error(sub_id)+time, df))
  ss_time = as.data.frame(unlist(mod$`Error: Within`))['Sum Sq1',]
  ss_error = as.data.frame(unlist(mod$`Error: Within`))['Sum Sq2',]
  eta = ss_time/(ss_time+ss_error)
  return(eta)
  }

get_sem <- function(dv_var, t1_df = test_data, t2_df = retest_data, merge_var = 'sub_id'){
  df = match_t1_t2(dv_var, t1_df = t1_df, t2_df = t2_df, merge_var = merge_var)
  mod = summary(aov(score~Error(sub_id)+time, df))
  ms_error = as.data.frame(unlist(mod$`Error: Within`))['Mean Sq2',]
  sem = sqrt(ms_error)
  return(sem)
}
```

>>>>

```{r echo=FALSE}
#Convenience functions to make prettier interactive histograms
get_labels = function(plot_df, ref_df, bin_col, group_col){

@@

```{r}
match_t1_t2 <- function(dv_var, t1_df = retest_subs_test_data, t2_df = retest_data, merge_var = 'sub_id'){
  df = merge(t1_df[,c(merge_var, dv_var)], t2_df[,c(merge_var, dv_var)], by = merge_var)
  df = df %>% 
    na.omit()%>%
    gather(dv, score, -sub_id) %>%
    mutate(time = ifelse(grepl('\\.x', dv), 1, ifelse(grepl('\\.y', dv), 2, NA))) %>%
    separate(dv, c("dv", "drop"), sep='\\.([^.]*)$') %>%
    select(-drop)
   return(df)
}

get_icc <- function(dv_var, t1_df = retest_subs_test_data, t2_df = retest_data, merge_var = 'sub_id'){
  df = match_t1_t2(dv_var, t1_df = t1_df, t2_df = t2_df, merge_var = merge_var)
  df = df %>% spread(time, score) %>% select(-dv, -sub_id)
  icc = ICC(df)
  icc_3k = icc$results['Average_fixed_raters', 'ICC']
  return(icc_3k)
  }

get_eta <- function(dv_var, t1_df = retest_subs_test_data, t2_df = retest_data, merge_var = 'sub_id'){
  df = match_t1_t2(dv_var, t1_df = t1_df, t2_df = t2_df, merge_var = merge_var)
  mod = summary(aov(score~Error(sub_id)+time, df))
  ss_time = as.data.frame(unlist(mod$`Error: Within`))['Sum Sq1',]
  ss_error = as.data.frame(unlist(mod$`Error: Within`))['Sum Sq2',]
  eta = ss_time/(ss_time+ss_error)
  return(eta)
  }

get_sem <- function(dv_var, t1_df = retest_subs_test_data, t2_df = retest_data, merge_var = 'sub_id'){
  df = match_t1_t2(dv_var, t1_df = t1_df, t2_df = t2_df, merge_var = merge_var)
  mod = summary(aov(score~Error(sub_id)+time, df))
  ms_error = as.data.frame(unlist(mod$`Error: Within`))['Mean Sq2',]
  sem = sqrt(ms_error)
  return(sem)
}
```
